Last glacial cycle glacier erosion potential in the Alps

### 2021-05-23 articles/erosion/alps-erosion.tex
Update hypsogram fig caption for new histograms.

    \begin{figure*}
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption{%
        \textbf{(a)} Modelled erosion rate ``hypsogram'', showing the geometric
          mean of (non-zero) modelled erosion rates in 10-m elevation bands
          across the entire model domain and its time evolution. The histogram
          to the side shows the distribution of topography in the model domain.
        \textbf{(b)} Same as Fig.~\ref{fig:cumulative}b.
      \todo{%
        test cutting the hypsogram below a minimum number of grid cells,
        try and compute cumulative erosion by elevation bins.}}
      \label{fig:hypsogram}
    \end{figure*}

>>>>

    \begin{figure*}
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption{%
        \textbf{(a)} Potential erosion rate ``hypsogram'', showing the
          geometric mean of (non-zero) modelled rates in 10-m elevation bands
          across the entire model domain and its time evolution.
        \textbf{(b)} Distribution of model domain bedrock topography (grey
          bars) and glaciated topography (blue bars) in 100-m elevation bands,
          and the corresponding cumulative potential erosion volume (brown
          line).
        \textbf{(c)} Same as Fig.~\ref{fig:cumulative}b.
        \todo{fix labels, test hatching below a minimum number of grid cells}}
      \label{fig:hypsogram}
    \end{figure*}
